### 2022-06-28 input/experiments.tex
meow

\newcommand{\FIGSCALE}{0.48}

@@

%To answer questions such as: what is the overhead of reaching
%consistent partitioning using \NAME in large scale networks and is
%\NAME relevant in Edge infrastructures where \processes are
%geo-distributed into clusters?
In this section, we discuss the evaluations of \NAME we conducted on top of
PeerSim, a simulator to
evaluate and assess distributed algorithms in large scale
networks~\cite{montresor2009peersim}. All the code is available on the
Github platform at \mbox{\url{https://github.com/ane-wane/as-cast}}.

@@

We build a network comprising 10k \processes. First, we chain
\processes together, then we add another link per
\process to another random \process. Since links are bidirectional,
each \process has 4 communication links on average. We set the latency
of links between 20 and 40 ms at random following a uniform
distribution.
%
To favor more concurrent operations, we voluntary set
weights and latency to different values: each link has a weight
between 5 and 15 set randomly using a uniform distribution. This
allows nodes to receive messages in a different order than their
respective shortest path generating more messages to reach consistent
partitioning.

@@

\noindent We measure the average number of messages generated per
\process per second; and the time before reaching consistent
partitioning after adding or removing a partition.

\begin{figure*}[t]
  \subfloat[\label{fig:complexity}Dynamic consistent partitioning overhead of \NAME.]{
    \includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_complexity.pdf} 
  }
  \hspace{5pt}
  \subfloat[\label{fig:geant}Partitioning overhead of 2
    clusters connected by a long distance link.]{
    \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_geant.pdf}
  }
  \caption{\TODO{\NAME overhead}.}
\end{figure*}

%% \begin{figure}[t]
%%   \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_complexity.pdf}
%%   \caption{\label{fig:complexity}Dynamic consistent partitioning overhead of \NAME.}

%%   %% \caption{\label{fig:complexity}Cumulative average number of messages
%%   %%   per process in a network comprising 10k processes; along with the
%%   %%   duration before reaching consistent partitioning after adding or
%%   %%   removing a partition, totaling 100 new partition then removed.}
%% \end{figure}

@@

\noindent Figure~\ref{fig:complexity} confirms that \NAME's overhead
depends on the size of partitions. In this scenario, it empirically
corresponds to a complexity in terms of number of messages of
$\mathcal{O}(\frac{|E|}{|V|\cdot|P|})$ where $E$ is the number of
links, $V$ is the number of \processes, and $P$ is the number of
partitions. In other terms, the $p^{th}$ partition contains $1/p$
\processes and reduces the size of closest partitions so every
partition has $1/p$ \processes on average.

@@

\noindent Figure~\ref{fig:complexity} also confirms that \NAME's
delete operations are roughly twice as expensive as creation
ones. Indeed, the top part of the figure shows that after 21 seconds,
when the experiment involves removals, traffic includes both
$\alpha$ and $\delta$ messages. The latter aims at removing stale
information and triggering competition while the former aims at
updating shortest paths. As corollary, the convergence time increases,
for $\delta$ messages must reach the partition borders before sound
competitors propagate their partition. It is worth noting that this
delete operation involves concurrency: removals still propagate while
the competition has started.
%%is already partially triggered and propagating.

@@

%% \begin{figure}[t]
%%   \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_geant.pdf}
%%   \caption{\label{fig:geant}Partitioning overhead of 2
%%     clusters connected by a long distance link.}
%% \end{figure}

>>>>

\newcommand{\FIGSCALE}{0.68}

@@

%To answer questions such as: what is the overhead of reaching
%consistent partitioning using \NAME in large scale networks and is
%\NAME relevant in Edge infrastructures where \processes are
%geo-distributed into clusters?
In this section, we discuss the evaluations of \NAME we conducted on top of
PeerSim, a simulator to
evaluate and assess distributed algorithms in large scale
networks~\cite{montresor2009peersim}. All the code is available % on % the
%Github platform
at \mbox{\url{https://github.com/ane-wane/as-cast}}.

@@

We build a network comprising 10k \processes. First, we chain
\processes together, then we add another link per
\process to another random \process. Since links are bidirectional,
each \process has 4 communication links on average. We set the latency
of links between 20 and 40 ms at random following a uniform
distribution.
%
To favor more concurrent operations, we % voluntary
set
weights and latency to different values: each link has a weight
between 5 and 15 set randomly using a uniform distribution. This
allows nodes to receive messages in different orders, % than their
% respective shortest path
therefore generating more messages to reach consistent
partitioning.

@@

\noindent We measure the average number of messages % generated
per
\process per second; and the time before reaching consistent
partitioning after adding or removing a partition.

%% \begin{figure*}[t]
%%   \subfloat[\label{fig:complexity}Dynamic consistent partitioning overhead of \NAME.]{
%%     \includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_complexity.pdf} 
%%   }
%%   \hspace{5pt}
%%   \subfloat[\label{fig:geant}Partitioning overhead of 2
%%     clusters connected by a long distance link.]{
%%     \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_geant.pdf}
%%   }
%%   \caption{\TODO{\NAME overhead}.}
%% \end{figure*}

\begin{figure}[t]
  \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_complexity.pdf}
  \caption{\label{fig:complexity}Dynamic consistent partitioning overhead of \NAME.}

%%   %% \caption{\label{fig:complexity}Cumulative average number of messages
%%   %%   per process in a network comprising 10k processes; along with the
%%   %%   duration before reaching consistent partitioning after adding or
%%   %%   removing a partition, totaling 100 new partition then removed.}
\end{figure}

@@

\noindent Figure~\ref{fig:complexity} confirms that \NAME's overhead
depends on the size of partitions. % In this scenario,
This % empirically
corresponds to a complexity in terms of number of messages of
$\mathcal{O}(\frac{|E|}{|V|\cdot|P|})$ where $E$ is the number of
links, $V$ is the number of \processes, and $P$ is the number of
partitions. In other terms, the $p^{th}$ partition contains $1/p$
\processes and reduces the size of closest partitions so every
partition has $1/p$ \processes on average.

@@

\noindent Figure~\ref{fig:complexity} also confirms that \NAME's
delete operations are roughly twice as expensive as creation
ones. Indeed, the top part of the figure shows that after 21 seconds,
when the experiment involves removals, traffic includes both
$\alpha$ and $\delta$ messages. The latter aims at removing stale
information and triggering competition while the former aims at
updating shortest paths. As corollary, the convergence time increases,
for $\delta$ messages must reach the partition borders before sound
competitors propagate their partition. % It is worth noting that
This
delete operation involves concurrency: removals still propagate while
the competition has started.
%%is already partially triggered and propagating.

@@

\begin{figure}[t]
  \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_geant.pdf}
  \caption{\label{fig:geant}Partitioning overhead of 2
    clusters connected by a long distance link.}
\end{figure}
